So, the story opens with the protagonist, probably the titular character
waking up in some highly familiar setting (e.g. his bedroom)
but feeling like something has been fundamentally altered. something...shifted.
His day goes normally enough, then he starts finding messages, possibly notes?
possibly whispered voicemails? or mysterious phonecalls \A(voices in his
head). \E There's no clear struggle driving the plot, just a vague feeling of 
tension and uncertainty. The messages are mostly devoid of useful content, 
just ``do you feel it? do you feel it coming? are you ready? soon...soon...soon..."
The day concludes and he goes to sleep again and wakes up in holy-shit-where-am-I 
land riding on a horse next to a small gnome-looking creature on a pig and 
something that looks like an ostrich running alongside them \A(hahha we can
ignore this part if you want)\E which comes as a bit of a surprise.
The voice from before (I'm going with a combination of notes and 
whispered voicemails) speaks to him again, slightly more clearly, 
it's noticeably a woman's voice, now. \\
``Don't panic. you don't want to fall off your house, do you? You know how to 
ride it, don't worry. Keep riding without saying anything until you crest the 
next hill and go to the inn. You'll learn more there". Not too excited to listen 
to her, but in the absence of any other clear direction or any sort of clue as 
to what's going on, the man does as she suggested
continuing to ride down the trail atop of what he firmly believes to be the only 
horse he's ever touched. The man is stunned by his ability to keep his seat atop 
the animal. The gnome glances at him from his pig-saddle but says nothing. Nearing 
the top of the hill, they see a vast checkerboard expanse of forests and fields 
spread out before them, with a lone building at the base of the hill as a 
testament to the existence of civilization as they near the inn. A youth comes to 
take the pig and horse to the stable, the gnome flipping him a gold coin as 
they make their way through the front door. As he enters, the man is overwhelmed 
by the cacophony within, hearing the clamoring of men at the bar mixed in with 
the banging of beer steins, drinking songs, and the nasal voice of a troubadour
through the commotion. In a corner, they see a petite figure sitting in a
corner. The gnome leads the party to join her at the table.
From this closer proximity, the man can see the dark-skinned face of a woman 
tattooed what he intuitively recognizes as the mark of the mage clan \\
edit* this is getting out of hand. \\

=]
