\chapter*{Discarded Thoughts}

\section*{Potentially Worth Revisiting Someday}

Idle Musings (for general consumption), just to flesh things out a bit.  There are two worlds that exist simultaneously. This does not present any problems.  Some climactic thing happens and hitches two bodies together to one consciousness.  It may or may not have relied on a previous connection between the two bodies (I'm leaning towards just not explaining it very thoroughly, at least not yet). This connection happened right around the start of the story? and the two consciousnesses somehow merged into one consciousness and then the consciousness started switching bodies. that's that thing. \\


Must have a fumble-fingered grasp of everything at beginning of transition to new world, brought to the fore by either adrenaline or by what seems to him as being guesswork and intuition. \\

Some crazy stuff is going on w/ how magic is manifesting in animals (magic is randomly distributed between humans and animals, humans manifest as spellcasters, animals manifest as being...special animals? doesn't appear to be genetic).  Somewhere there is a bear character.  So, the animals are generally benign, or at least act like animals, but the magic ones are coming out twisted and they're trying to narrow down on the location from whence they're stemming?  Possibly that's how why they warped me in, some sort of statistical analysis thing? or something? anyway, this seems good. THE BEAR is a mutated animal that seems far more intelligent than other animals and seems to be able to communicate? no, it seems to be able to $plan^*$ we run into the bear and get freaked out because it somethingsomethingsomething and then it reacts to us in an incredibly intelligent fashion and THEN we catch on, the bear is still learning how to be intelligent so it's not just out there acting like a person. Awesome. \\

The methods in which magic could be used made it very easy to travel (wheeled cart w/ momentum transfer?) because magicians can loop their spells into themselves in a sort of self-sustaining fashion, but only in a taxing manner (so livestock aren't replaced, really, but it means that mages are ridiculously useful to farmers for the harvest, and useful to everybody as transport).

\section*{Probably Not Worth Revisiting but Preserved for Posterity}

Normal life. as an engineer of some sort? useful knowledge required. not sure what kind yet, will have to find out once I figure out what the conflict is. \\

Better description of a day to establish his bona fides as an a) intelligent person 
\begin{itemize}
\item[b)] someone who takes changes in stride 
\item[c)] someone who's very athletic.  
\item[b)] being said, he gets more and more unsettled as the day goes on w\/ the mysterious messages
\end{itemize}
Goes to sleep. Wakes up on horse. Companions of some sort? i don't think I want a gnome or an ostrich thing, that was weird. Men would be best. Elves, etc., too many of them. Let's just keep everyone human.

\section*{Rough Outline}

lived in what we think of as a normal world
pulled into the new world, utter confusion. \\
meet up with the other members of the party. the 2 initial companions never say anything to suggest that the protagonist isn't exactly what they expect. the mage is clearly the one who was talking to him (somehow) is not interested in explaining right away. Probably for a reason (he gets captured in a bit? mind readers? freak him out too much?).\\ As he goes along, he has all the skills you'd expect of a master swordsman / traveler. horse-riding, archery \& tracking, hand-to-hand fighting--basically he's Aragorn.  Must have been brought for a reason, get to that later. Begin travelling, other two go hunting regularly, you stay with the mage for basic outline of what's going on.  \\\\


They live in a civilization w\/ magic, which has an unknown source but some people can simply access it and use it a functional muscle. (some people are weak/others strong, get better by training, can learn how to do new things with it via experimentation with energy somehow or another. Limit it to energy-based things?).   \\

MAGE POWERS
--can communicate with the protagonist
