\chapter*{Layer 1: Life} \section*{The Nature of the life on the world}

\R Every living thing in the world has a nature of some sort, like, a spiritual
nature.  Humans are intelligent, dogs are ...happy, I don't know, pigs are
hungry, dolphins are clever (this is fantasy, btw). \\ Each creature has its own
spellcasting style, or at least its own magical style - details of this are
unclear at present. \\ You can gain aspects of other creatures
styles/abilities/nature by doing human-animal transplants and converting part of
your body into a part of the animal body. \\ Increasing/altering your powers,
with the tradeoff of losing some of the human aspect of yourself. \\ the twist:
inanimate objects also have their own nature, so you could, say, make yourself a
hand out of granite and it'd give you something new as well. \\ \\

[The northern continent]  is where we are and where the Evil Lord of Evil and a
few scattered other people wound up).  I'm not sure how this is going to work
with Nature ending up being a participant, we'll have to figure out exactly how
the Southerners end up interacting with us and the Evil Lord of Evil. 

\A okay. So people can’t physically travel across the wasteland. However, nature
is connected. Animals can travel. There are a couple of solutions to this. One
is that it travels through the earth somehow. Alternatively, some animal carries
the human parts over.

\R thought: someone finds an animal somewhere whose magical ability lends itself
towards traveling across the wasteland.  If we have a sufficiently varied group
of animals who are extremely limited in number (either by real scarcity or just
by difficulty in finding them) there could be an actual industry in capturing
said animals, as well as people having things comparable to superpowers because
they found one ridiculous animal.  I'm not a big fan of either option, as
'traveling through the earth' is a bit weird and I don't know why an animal
would carry the human parts.  Possibly we could figure something out w.r.t.
disposal procedures that's something like "they dump the remains into an
underground river that comes out who-knows-where so they just don't care about
it, and then it accumulates"?  was that what you meant? \\\\

FOR MOST PEOPLE once they have a cat arm, whatever, it's a cat arm, can't really
do anything about it. you now have 80\% human 20\% cat, and this is the case
   EVEN IF YOU LOSE THE CAT ARM AND NOW HAVE A STUMP AGAIN. it's just the way
   your body's magic is now.

\A So like, if you lose the cat arm, do you also lose the cat magic?

\R umm...depends.  I was yammering at one point about how the cat arm is what
casts cat-magic-imbued things, in which case, yes.  otherwise, no.  Also, I
think the way I'm picturing this happening is that we cast magic that makes the
cat arm the right size for the human because otherwise it'd look a bit goofy. i
demand aesthetic excellence.

\A Aesthetic excellence is of primary importance. We need to figure out how the
different abilities affect magic. Thats the first thing. 

\R We are a part of a thriving but agrarian society--everyone is relatively
satisfied but things are still happily progressing (no stagnation).  Magic is
combined with technology (we can cast spells that are active in perpetuity, but
only on inanimate things, and the complexity is very limited. which means you
can potentially have a whole lot of limited-complexity things that combine to be
one big-complexity things (e.g. computers)).  \\ Given previous discussion of
how magic works, I think it's out of reach to do something like massively reduce
friction for a particular wheel, or something like that, which'd be reallly
helpful for farmers and transportation and stuff.  However, we could do things
like : public transportation where the (wagon?) wheels are enchanted to rotate
with a certain amount of energy, and at the boarding stations, you adjust the
tracks in which they run to have a much higher coefficient of friction so the
wagon slows down for a bit while people hop on and keep on going. there's
gimmicks like that we can play with.  Also, things like plows could be magicked
(some gears to make it travel down the path that rotate with X energy, other
gears that rotate at a different rate to cause the plow to turn the appropriate
time to till the fields).  Long-distance communications could potentially be
magicked (i don't think they'll need to do stuff with telephones, at least not
yet; just throw up a bunch of high ziplines and run canisters along them to
bring messages).  Counting would be definitely magickable (something that shifts
beads (in the manner of an abacus?) when the mass of the thing they're attached
to increases by the amount of whatever-is-being-added. This is the kind of thing
I'm thinking of.  I don't want to get all the way to computers yet (if the Earth
is only in the middle ages, this world can't be anywhere near computerized
technology; I'm just trying to illustrate the kind of things that I'm
picturing).  I don't anticipate these things being used in warfare--i might not
anticipate any warfare here at all, life is way too good in this society. \\ 

Figuring out the mechanics of this later: somehow or another, we are imbuing the
landscape with our magic.  The landscape should become a non-identifiable player
in the coming conflict. The bear gets to play here. 

\A I think I don't \textit{quite} get what you mean by environment here. Does it
like, infuse random creatures with abilities? This might help sort out the whole
``a predefined list of spells thing". So is it like a DM/God thing or just like,
nature? 

\R think like mother nature type of thing.  somehow something in nature (think
of it as being akin to one of those groves of trees that's actually all one
giant organism) has the ability to affect the nature (bloody homonyms) of things
around it. \\ \\

Maybe the only characteristic that humans have is being intelligent? i think
that's only fair. it's also extra incentive from a power standpoint to merge
with other creatures but a fascinating tradeoff since you become less, yknow,
smart. so that'd turn out sorta like my take on your merging idea where people
become less human it also simplifies the way that the environment starts to take
on a personality, because the magic it's getting from people is explicitly
intelligence. no need to deal with wonky metaphysics of how having human parts
gives you consciousness.  it also might be appropriate to give most animals that
fit into a given environmental niche a very similar characteristic (simplifies
the difficulty of having to generate seven million different characteristics).
so, rats \& mice \& chipmunks all have basically the same thing going on for them.
it'll probably be hard to think of things that don't upset the balance of power
too much. the food chain will look very interesting with explosions happening
all through it. 

\A I am not convinced about this. Presumably we won't discuss \textit{every}
animal in the story. I think it would be really difficult to segregate like
that. Also, I am totally excited about explosions.

\R I mean, I certainly don't plan to discuss ALL of them, but the more animals
show up, the more realistic the world is, and the more opportunities it gives us
to expand the magical capabilities of the humans who can borrow other people's
magic. and I don't see why it's gonna be complicated to segregate? Even in this
world, prey animals have certain characteristics that are frequently shared
(e.g. extremely rapid gestation cycle, foraging habits, level of twitchiness and
paranoia about getting eaten) and predatory animals do as well (less breeding,
very pointy claws, exceptional sight/hearing, sharp pointy teeth) \\ maybe power
is related in some fashion to body mass? it seems like it'd be unfair to do it
most other ways. i think i'll go with that. insect characteristic is that masses
can generate one super-big spell instead of lots of little ones, otherwise
they'd suck too much.

\R Okay, so I really like the idea of single characteristics associated with
different creatures. And how that manifests itself in their abilities. But,
presumably they have different abilities. So one thought I had was, that humans
are rare. And the whole figuring out how to reverse the process is a
manifestation of the intelligence. So is the evil lord of evils getting random
creatures to merge together. (This drawback here is that he can’t actually get
them to merge with humans, cause there arent very many). But then we can have
some other humans who just kind of do their own thing on the side and mess stuff
up for everyone else. (ie chaotic neutral). I am really excited about this one. 

\E
