\chapter*{Layer 2: And Everything}

\section*{The Aspects of Living that will be necessary for Story Development} 

\R 
\textbf{UNIVERSAL LAWS} \\
Bear! \\
Magic! \\
Yey! \\ \\ \\


We are going with my earlier proposition of 'we can adopt other species' magic by taking on a part of that species'. \\
We can also potentially use your merging proposal, I liked that: \\
THE REASON WE ARE THE PROTAGONIST IS BECAUSE
we have developed (innate ability? some spell we figured out? something else?) the ability to reverse the process in some convenient fashion. \\ 
we can reverse that as needed $\rightarrow$ at any point in time we can go back to being 100\% human by doing the appropriate thing. \\
i think this is a good idea because it means that we can figure out from a first-person perspective what the hell it means when we have all these different species going on. lots of mixing and matching and weird stuff to play with.

\A Yes, this is cool. I like this. 

\R As discussed above!  I am also quite excited about this.  how do you feel about having the northern continent have something like 9 people in it, one for each of the permutations of [chaotic \& evil, good \& evil, neutral]?  either way, yes, this sounds wonderful.  Again, I think figuring out how to reverse the process is broadly innate to us, although that won't be clear for a long time since we don't have access to the majority of the humans populating the magical world. \\ \\

Enter the Evil Lord of Evil \\

the Evil Lord of Evil is the first person to start using the magic of body-shifting in an explicitly hostile and human-abusive fashion.  Developing...some sort of army? he lives out in the wilderness where he experimented and figured out how to get a whole lot of barely-human-mostly-animal-but-just-enough-human-to-follow-instructions people.  or something like that.  his motives are unclear but I think we can probably go with the Joker principle. --some men just want to watch the world burn ($\langle$ Random blob of flesh that Russ thinks is a heart and can be found \href{http://fatnewsfeed.com/wordpress/wp-content/uploads/2010/10/heart\_cropped.jpg}{here} $\rangle$ this movie, btw) 

\A How. Like, how does he do it? When you suggested this I pictured like a guy with a castle and a huge army. And they captured people and got them merge with different things ect. But, you seem to have a different picture. 

\R Huge animal army? since humans are no longer eligible.  I propose that he is considering trying to conquer the Earth but gets sidetracked by 1) us and the other people on the continent and 2) the eventual discovery of the other people on the south of the continent. \\

Our interest as a protagonist is primarily scientific, at least at the outset.  we're not necessarily concerned with the politics of the situation (the Evil Lord of Evil can do what he wants) we just want to know how he's doing it.  We are a super-boss because of what we can do (e.g. go 80\% bird, fly halfway into his territory, turn back, turn into 75\% kangaroo, hop the rest of the way, whatever).  

\A I think details need to be hashed out here. I mean, presumably he need to find the animal. If he reverses it, what happens to the animal?

\R noo idea! maybe we carry around a bunch of animal corpses in a bag. I'm flexible on this one. \\

However, he starts playing mean with us and we have to start dealing with that.  

\A What is his motivation for doing this?

\R we're mucking around in his business, and he's chaotic evil? \\

he starts to piss us off which means we have a vendetta, that's enough of a driving force for me. \\

Somewhere in here (did I mention that he's in the wilderness? I think I did) things start happening (we get attacked by bizarre creatures) and figure it's more of his crazy stuff going on and are really intrigued. Turns out it's not him. The environment is messing around. Somewhere in here there's a bear.

\A See above question. (where you first discussed the environment)

\R so, I don't know if we're an anti-hero or a hero (if we're a hero, we need a hero turn at some point. if we're an anti-hero, we can go with being chaotic good and doing whatever we want).  

\A Now we just need a real conflict, and we are good to go. Is there a girl? \\
Also, did we entirely give up on multiple realities?

\R Conflict: we appear on the horse from Earth. we don't know what the hell is going on. we figure out that we have powers and we are extremely disturbed by the fact that, while we are initially encountering only normal wildlife that seems familiar from Earth, once in a while we come upon freak combinations of creatures (from the Evil Lord of Evil and perhaps from the other dudes in the Northern Lands?) which are a clear sign (along with the fact that we can cast magic spells) that we are not in Kansas anymore, Toto.  we venture onwards and see increasing quantities of the mutant creatures (heading towards the ELoE's territory) that we are willing to press through because we want to know what the hell is going on. ELoE is interested in returning to the Earth and trying to conquer it; we're down with the "trying to get back to earth" part but are not interested in helping him conquer it, because he's clearly chaotic evil. Eventually we run into the Lawful Neutral guy who explains everything to us and the Good Neutral guy who teaches us, and the Lawful Good guy who we piss off because we're chaotic (good/neutral) and we don't sync up with him forever (i really want to piss off the lawful good guy, please please please?)

