Haikus are a fun intro. \\
I have seen this world \\
I have seen its fickle ways \\
It can't surprise me 
\pagebreak

Rocking... back and forth... \\
Another morning. \\
Damn it. \\\\
Sebastian groggily rolled over, slapping at his alarm clock. The infernal 
beeping stopped abruptly as his blows finally struck their target, allowing him
the pleasure of waking up to the various noises his surroundings had to offer.
Just like every other morning, this was soon inturupted
by Sebastian’s low, expletive-filled mumbling about the 
general unfairness of the universe and the more specific injustice of 
having to get up with the sun. All he wanted was to just stay in bed. 
He considered it, only to be inturupted by a loud knock on his
door. 

\begin{quote} 
\A Make this sound more sailor-like: \E \\
``Sebastian, you are needed on the deck, immidiatly"
\end{quote}
       
The boat listed to starboard as the crew stumbled, trying to keep their balance.
Sebastian desparately spun the wheel, hoping to stabilize the rudder and level
out the ship. He was surprised that he had managed to sleep so soundly through
all the turbulence. He had been doing this a long time. The boy who had the
night shift was fairly new at this and the goods they carried, though tightly
strapped down, were fragile enough that profits could depend on their
ability to keep the ship even. His ability to keep the ship even. 
Being the helmsman for a merchant ship bore with it certain benefits, but if
something were to go wrong, he was the most obvious target for blame. He should
not be worried, he had been doing this a long time. But something was different
today. \\

Sebastian knew something as amiss when the boat
lurched, and Charles, in the crow's nest, nearly lost his footing. Sebastian had
seen Charles man his post during gales, hurricanes, ship-to-ship combat and
every other situation a merchant ship could find itself in, and not once had he
shown any sign of difficulty in keeping his balance. Somewhat unnerved,
Sebastian gently rotated the wheel to reassure himself that the lurch was simply
a moment of high spirits by the Lady of the Ocean -- he had seen stranger things
happen when the gods decided to play games \R(can I change this to dice?)\E. His peace of mind was shattered
when the rudder resisted him, as if the water had started to solidify around the
ship. \R okay, so I was thinking that he could start hearing voices at this
point - re: Appendix1. This could be the beginning of a rough day where he has to be
super-navigator and save the day, and possibly dismiss the voices as just being his
subconscious acting up due to stress. But this is actually our NE character (who
we decided he would encounter first, though the actual premise of the encounter
was not specified.) This is my proposal. She found a way to communicate with the
other world and is now just messing. At the end of the day he goes to bed. This
still needs to be filled in, but I am skipping to the next day now. \\ \E

\begin{quote}
``Don't panic. You don't want to fall off your house, do you? You know how to
ride it, don't worry. Keep riding without saying anything until you crest the
next hill and go to the inn. You'll learn more there"
\end{quote}
It was her again. Sebastian was not too excited about the fact that he was still
listening to this strange voice in his head, but in the absence of any other clear
direction or any sort of clue as to what's going on, he did as she suggested.
Anyway, there were more important things at stake. What the hell was
he doing on a what he firmly believes to be the only horse he's ever touched. 
He stunned by his ability to keep his seat atop the animal.  \\

NOTE: \\

I propose to reuse the ``rocking...back and forth..." as an intro to when he's on
the horse, gradually waking up, rocking back and forth, flashing back to the
ship thing and then ``what the fuck i'm on a horse what is this shit"\\ 
